Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-08-10 src/article.tex
Tested on Ubuntu
Add track changes LaTeX package
List software dependencies in description section

% Load packages
\usepackage{cite} % Make references as [1-4], not [1,2,3,4]
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}

@@

  \begin{description}
    \item[Project name:] Scaffolder v0.4.1, Scaffolder Tools v0.1.2
    \item[Project home page:] \scaffolder
    \item[Operating system:] Platform Independent. Tested on Mac OS X and
    Debian.
    \item[Programming language:] Ruby
    \item[Other requirements:] RubyGems
    \item[License:] MIT
    \item[Any restrictions to use by non-academics:] None
  \end{description}

>>>>

% Load packages
\usepackage{cite} % Make references as [1-4], not [1,2,3,4]
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage{trackchanges}
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}

@@

  \begin{description}
    \item[Project name:] Scaffolder v0.4.1, Scaffolder Tools v0.1.2
    \item[Project home page:] \scaffolder
    \item[Operating system:] Platform Independent. Tested on Mac OS X and
    Ubuntu.
    \item[Programming language:] Ruby
    \item[Other requirements:] \change{RubyGems}{RubyGems package management
    software and the following libraries: BioRuby and confligliere. A full
    list of development dependencies can be found in the Gemfile in the base
    directory of each project.}
    \item[License:] MIT
    \item[Any restrictions to use by non-academics:] None
  \end{description}
